---
title: "Rmerp"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The Rmerp package is a set of functions that facilitate
the collation of marine data from multiple sources for MERP
users. This is a functional but basic version of the package. Further
developments and improvements will come from interacting with 
users as they run into bugs or need additional functionalities.
Any requests or problems can be reported by clicking on the issues
tab on github.


Below are some examples of what can be done with the currently available fuctins

```{r, echo = FALSE}

```

Installation
The Rmerp package is solely accessible to MERP members. Installation from R
requires an authenticating key. Please see document on Strathcloud to.

```{r, echo = FALSE}
library(devtools)
devtools::install_github(remsamp/Rmerp, )
library(Rmerp)
```
  
)

